Particle Swarm Optimization for Passivation of Steel Substrate with Zirconium Oxide

### 2024-10-29 doc/presentations/defensio/defense.tex
final defense.tex

\begin{graphicsFrame}{Thin-Film Photovoltaics: CIGS modules}{}{0.1}{}{cigs_mod}{}
\end{graphicsFrame}

@@

		\vspace{1em}
		\begin{itemize}
			\item Tape Casting
				\begin{itemize}
					\item temperature: 40-\SI{80}{\degreeCelsius}
					\item blade speed: 10-\SI{20}{\milli\meter/\second}
				\end{itemize}
				\vspace{1em}
			\item Calcination
				\begin{itemize}
					\item temperature: 300-\SI{500}{\degreeCelsius}
					\item heating rate: 2-\SI{12}{\degreeCelsius/\hour}
				\end{itemize}
		\end{itemize}
\end{graphicsFrame}

@@

	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
\begin{graphicsFrame}{Current-Voltage characteristics}{}{0.37}{left}{iv-noi}{}
	\vspace{2em}
	\begin{itemize}
		\item voltage sweep
		\vspace{.5em}
		\item \SI{10}{\milli\volt} steps
		\vspace{.5em}
		\item very low current 
		\vspace{.5em}
		\item low conductivity 
		\vspace{.5em}
		\item high resistance 
	\end{itemize}
\end{graphicsFrame}
\begin{graphicsFrame}{Current-Voltage characteristics II}{}{0.37}{left}{iv-log}{}
	\vspace{2em}
	\begin{itemize}
		\item all measurements of single sample
		\vspace{.5em}
		\item huge range 
		\vspace{.5em}
		\item low current
		\vspace{.5em}
		\item high current
	\end{itemize}
\end{graphicsFrame}

@@

\begin{frame}{Input Variables for Optimisation}
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
		$c_{zr}$ [\SI{22}{\milli\mol/\liter}]	&$n_L$	&$T_{C}$[\SI{}{\degreeCelsius}]	&$v_{C}$[\SI{}{\milli\meter/\second}]	&$T_{cal}$[\SI{}{\degreeCelsius}]	&$v_{cal}$[\SI{}{\degreeCelsius/\hour}]	\\
		\hline
		\pause
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}
\end{frame}

%	\begin{itemize}
%		\item Aluminium Contact through mask
%		\item Silver paste
%	\end{itemize}
%\end{frame}
%07. results measuring 
%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
	% - EMMA 
%08. results EMMA 
%\begin{frame}{Pin Hole Density}\begin{figure}\includegraphics[width=.66\textwidth]{figures/phd.png}\end{figure}\end{frame}
%\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
\begin{frame}{PSO generations}\begin{figure}\includegraphics[width=.96\textwidth]{figures/emma-gen.png}\end{figure}\end{frame}
%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
	% - gen 
%09. comparison with other statistics 
	% - comparing with other stats

@@

%10. summary 
\begin{frame}{Summary}
	\vspace{2em}
	\begin{itemize}
		\item new recipe for dense \ch{ZrO2}
			\vspace{.5em}
		\item optimzed method with PSO
	\end{itemize}
\end{frame}
	% - created ZrO2
	% - optimized with EMMA
	% - double checked with stats
%11. conclusion 
%12. end

>>>>

%\begin{graphicsFrame}{Thin-Film Photovoltaics: CIGS modules}{}{0.1}{}{cigs_mod}{}
	\begin{frame}{Thin-Film Photovoltaics: CIGS modules}
	\begin{itemize}
		\item high absorption coefficient
		\item connected in series 
		\item substrate:
			\begin{itemize}
				\item must be insulating 
				\item mostly glass
			\end{itemize}
	\end{itemize}
	\begin{figure}
		\includegraphics[width=.9\textwidth]{figures/cigs_mod.png}
	\end{figure}
\end{frame}
%\end{graphicsFrame}

@@

		\vspace{1em}
		\begin{itemize}
			\item Tape Casting
				\begin{itemize}
					\item temperature: 40-80\SI{}{\degreeCelsius}
					\item blade speed: 10-20\SI{}{\milli\meter/\second}
				\end{itemize}
				\vspace{1em}
			\item Calcination
				\begin{itemize}
					\item temperature: 300-500\SI{}{\degreeCelsius}
					\item heating rate: 2-18\SI{}{\degreeCelsius/\minute}
				\end{itemize}
		\end{itemize}
\end{graphicsFrame}

@@

	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
\begin{graphicsFrame}{Current-Voltage characteristics}{}{0.37}{left}{iv-noi}{}
	\vspace{2em}
	\begin{itemize}
		\item voltage sweep
		\vspace{.5em}
		\item 10\SI{}{\milli\volt} steps
		\vspace{.5em}
		\item very low current 
		\vspace{.5em}
		\item low conductivity 
		\vspace{.5em}
		\item high resistance 
	\end{itemize}
\end{graphicsFrame}
\begin{graphicsFrame}{Current-Voltage characteristics II}{}{0.37}{left}{iv-log}{}
	\vspace{2em}
	\begin{itemize}
		\item all measurements of single sample
		\vspace{.5em}
		\item huge range 
		\vspace{.5em}
		\item low current
		\vspace{.5em}
		\item high current
	\end{itemize}
\end{graphicsFrame}

@@

\begin{frame}{Input Variables for Optimisation}
	\begin{itemize}
		\item precursor solution concentration
		\item number of layers 
		\item coating temperature
		\item blade speed
		\item calcination temperature
		\item calcination heating rate
	\end{itemize}
\end{frame}

\begin{frame}{Input Variables for Optimisation}
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
		$c_{zr}$ [22\SI{}{\milli\mol/\liter}]	&$n_L$	&$T_{C}$[\SI{}{\degreeCelsius}]	&$v_{C}$[\SI{}{\milli\meter/\second}]	&$T_{cal}$[\SI{}{\degreeCelsius}]	&$v_{cal}$[\SI{}{\degreeCelsius/\minute}]	\\
		\hline
%		\pause
		2				&4		&40					&10				&300				&2	\\
		3				&6		&50					&12				&400				&6	\\
		4				&8		&60					&14				&500				&10	\\
		5				&10		&70					&16				&					&14	\\
						&12		&80					&18				&					&18	\\
						&		&					&20				&					& \\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}
\end{frame}

%	\begin{itemize}
%		\item Aluminium Contact through mask
%		\item Silver paste
%	\end{itemize}
%\end{frame}
%07. results measuring 
%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
	% - EMMA 
%08. results EMMA 
%\begin{frame}{Pin Hole Density}\begin{figure}\includegraphics[width=.66\textwidth]{figures/phd.png}\end{figure}\end{frame}
%\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
\begin{frame}{Particle Swarm Optimisation Iterations}
	\begin{itemize}
		\item metrics are reduced per generation
		\item model learned to represent data
	\end{itemize}
	\begin{figure}
		\includegraphics[width=.96\textwidth]{figures/emma-gen.png}
	\end{figure}
\end{frame}

%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
	% - gen 
%09. comparison with other statistics 
	% - comparing with other stats

@@

%10. summary 
\begin{frame}{Summary}
	\vspace{2em}
	\begin{itemize}
		\item found recipe for dense \ch{ZrO2} via sol-gel
			\vspace{.5em}
		\item prepared insulating \ch{ZrO2} layers
			\vspace{.5em}
		\item optimization chose correct input variables
	\end{itemize}
\end{frame}
	% - created ZrO2
	% - optimized with EMMA
	% - double checked with stats
%11. conclusion 
%12. end
